\newpage
\begin{thebibliography}{99}
\addcontentsline{toc}{section}{REFERENCES}
\bibitem{RF}
Breiman, Leo. "Random forests." \textit{Machine learning} 45.1 (2001): 5-32.
\bibitem{512}
Kutner, Michael H. 
\textit{Applied linear regression models. --4th ed.} Michael H. Kutner, Christopher J. Nachtsheim, John Neter.
\bibitem{Cook's Rule}
Bollen, Kenneth A.; Jackman, Robert W. (1990). Fox, John; Long, J. Scott, eds. 
\textit{Regression Diagnostics: An Expository Treatment of Outliers and Influential Cases. Modern Methods of Data Analysis.}
Newbury Park, CA: Sage. pp. 257–91. ISBN 0-8039-3366-5.
\bibitem{Deng}
Deng, Grace. "Analyzing the Risk of Mortgage Default" (2016)
\bibitem{Sirignano}
Sirignano, Justin. Sadhwani, Apaar. Giesecke, Kay. "Deep Learning for Mortgage Risk" (2015)
\bibitem{RGLM}
Song L, Langfelder P, Horvath S. (2013) Random generalized linear model: a highly accurate and interpretable ensemble predictor. BMC Bioinformatics 14:5 PMID: 23323760 DOI: 10.1186/1471-2105-14-5.
\bibitem{Stampede}
Stampede 2 User Guide. (2018) https://portal.tacc.utexas.edu/user-guides/stampede2
\bibitem{Fannie}
Mortgage Basics. https://www.knowyouroptions.com/buy/buying-process/qualify-for-a-mortgage/mortgage-basics
\bibitem{randomForest}
A. Liaw and M. Wiener (2002). Classification and Regression by
randomForest. R News 2(3), 18--22.
\bibitem{ranger}
Marvin N. Wright, Andreas Ziegler (2017). ranger: A Fast Implementation
of Random Forests for High Dimensional Data in C++ and R. Journal of
Statistical Software, 77(1), 1-17. doi:10.18637/jss.v077.i01
\bibitem{tidyverse}
Hadley Wickham (2017). tidyverse: Easily Install and Load the
'Tidyverse'. R package version 1.2.1.
https://CRAN.R-project.org/package=tidyverse
\bibitem{mapproj}
Doug McIlroy. Packaged for R by Ray Brownrigg, Thomas P Minka and
transition to Plan 9 codebase by Roger Bivand. (2017). mapproj: Map
Projections. R package version 1.2-5.
https://CRAN.R-project.org/package=mapproj
\bibitem{fiftystater}
William Murphy (2016). fiftystater: Map Data to Visualize the Fifty U.S.
States with Alaska and Hawaii Insets. R package version 1.0.1.
https://CRAN.R-project.org/package=fiftystater
\bibitem{zipcode}
Jeffrey Breen (2012). zipcode: U.S. ZIP Code database for geocoding. R
package version 1.0. https://CRAN.R-project.org/package=zipcode
\bibitem{ggmap}
D. Kahle and H. Wickham. ggmap: Spatial Visualization with ggplot2. The
R Journal, 5(1), 144-161. URL
http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf
\end{thebibliography}
